
\clearpage
\cleardoublepage

\chapter{Experiments \& Results}

\label{chap:experiments_results}

In this chapter, we will analyze the outcomes of our extensive experimentation with various map projections and their impact on the performance
of Convolutional Neural Networks (CNNs), specifically focusing on the U-Net architecture. By systematically applying these models to various types of
map projections. We aim to clarify the subtle impacts these projections have on the accuracy and efficiency of
geospatial data analysis. This inquiry is rooted in a comprehensive experimental structure devised to evaluate the model's capacity to forecast precipitation patterns
from geospatial data inputs, thereby furnishing valuable insights into the optimal utilization of CNNs in the realm of geospatial analysis.

% Through this section,
% we strive to bridge the divide between theoretical knowledge and practical implementation, making a significant contribution to the advancement of the field by
% highlighting potential avenues for future research.

% The experimentation is conducted on four different types of map projections, namely Cylindrical, Pseudocylindrical, Conic and Planar projections.
% Then we have selected four map projections in each of the main projection types.
% The U-Net model mentioned in \autoref{chap:approach} is trained for 20 epochs for each of the map projections. Initially 120 epochs were defined for the experimentation, for each of the models the phenomenon of overfitting started to occur over the training period, to mitigate the issue \textbf{early stopping} was deployed and each model was trained for 20 epochs.
% Mean absolute error (MAE) is used as a metric for the evaluation of the model.

% 16 geospatial raster datasets with the raster resolution of 240x240 were generated for the experimentation, via the process of creating rasters as mentioned in \autoref{chap:preprocess}. The loss and the metrics discussed in the result section are the average results, as for each map projection dataset the U-Net model is trained four times mitigating the issue of randomness in the network's parameters.

% The training of the models is displayed for all of the 4 cylindrical projections and 3 of the pseudocylindrical projections, and the values of the metrics used for the evaluation of the model is displayed in a tabular form.
% For the conic and the planar projections only the evaluation metrics are shown. In the end we will discuss the overall map projections.

\section{Experimental Setup}
The experimentation is carried out on a total of four distinct types of map projections, specifically Cylindrical, Pseudocylindrical, Conic, and Planar projections.
To ensure comprehensive coverage, I have carefully chosen four map projections within each of these main projection types, these projections are chosen on the distortions that these projections are trying to preserve.

\subsection{Early Stopping}
The U-Net model, as mentioned in \autoref{chap:approach}, undergoes a training process comprising 20 epochs for each of the map projections.
Originally, a total of 120 epochs were designated for the experimentation; however, it became apparent that the phenomenon of overfitting occurred throughout the
training period for each of the models. To address this challenge, the strategy of "early stopping" was deployed, resulting in the training of each model for a reduced
duration of 20 epochs.

\subsection{Performance Evaluation}
In order to evaluate the performance of the U-Net model, the mean absolute error (MAE) is employed as a metric. This metric serves as a reliable measure to gauge
the accuracy and precision of the model's predictions.
\subsection{Raster Generation}
Furthermore, a set of 32 geospatial raster datasets, each with a raster resolution of 240x240, were generated specifically for the purpose of these experiments, 16 geopotential height map projected rasters datasets and 16 precipitation map projected rasters datasets.
These datasets were created using the raster creation process detailed in \autoref{chap:preprocess}.
It is important to note that the reported loss and metrics discussed
in the results section represent average values. This is due to the fact that for each map projection dataset, the U-Net model is trained four times, thereby mitigating
the potential impact of random variations in the network's parameters.
\subsection{Model Training Analysis}
The training progress of the models is meticulously documented for all four cylindrical projections, three of the pseudocylindrical projections.
Additionally, the values of the evaluation metrics employed to assess the model's performance are presented in a concise tabular format.

However, for the conic and planar projections, only the evaluation metrics are showcased as these particular projections do not undergo the same level of detailed training
analysis.

Finally, following the presentation of the specific experimental results, a comprehensive discussion will be conducted to provide an overarching analysis of the
various map projections under consideration.

\clearpage
\input{text/chapters/chapter-8/cylindrical_projections.tex}
\clearpage
\input{text/chapters/chapter-8/pseudo_cylindrical_projections.tex}
\clearpage
\input{text/chapters/chapter-8/conic_projections.tex}

\clearpage
\input{text/chapters/chapter-8/plannar_projections.tex}


Now, I will compare each map projection type by the values of MAE observed during the training process.

\begin{table}[ht]
    \centering
    \caption{Summary of The Used Projection Types}
    \label{cylindrical_results_table}
    \renewcommand{\arraystretch}{1.2} % Adjusts the row height
    \begin{tabular}{|l|c|c|c|c|c|}
        \hline
        \rowcolor[gray]{0.9}
        \textbf{\emph{Projection Types}} & \textbf{\emph{Validation MAE}} \\ \hline
        Cylindrical                      & 0.49-0.51                      \\ \hline
        Pseudocylindrical                & 0.61-0.64                      \\ \hline
        Conic                            & 0.60-0.67                      \\ \hline
        Planar                           & 0.62-0.78                      \\ \hline
    \end{tabular}
\end{table}

\begin{itemize}
    \item The MAE values for the \textbf{cylindrical projections} were better as compared to the other types of the projections.
          The value of the MAE for all the cylindrical projections was around 0.50.
    \item The value of the metric for \textbf{pseudocylindrical projections} is increasing as compared to the cylindrical projections, The metric is performing worst in this case.
    \item The value of the metric for \textbf{conic projections} is increasing and the prediction of the precipitation are getting worst.
    \item \textbf{Planar projections} have shown the most results as the values are between 0.62 and 0.78.
\end{itemize}

The Cylindrical Projections have performed better then all of the projection types. Now I will conclude and propose the future endeavour for the search of a better representation of the Earth for the geospatial analysis.